Brain region specific differential expression analysis (all 7 regions/one region at a time)

### 2017-05-17 code/Rmd/regionLevelDiffExpAnlz.Rmd

  # Filter counts and covariates
  cnt = cnt[,cov$SampleID]

@@

  # Perform differential expression between case-control
  if(any(unique(cov$BrainRegion) %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(unique(cov$BrainRegion) %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else (any(unique(cov$BrainRegion) %in% c('CER', 'TCX'))) {
      varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI',
                        'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                        'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
    }
  } 
  contVar = 'Diagnosis'

@@

  # Perform differential expression between case-control in a gender specific manner
  cov$Diagnosis.Gender = factor(paste(cov$Diagnosis, cov$Gender, sep = '.'))
  if(any(unique(cov$BrainRegion) %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(unique(cov$BrainRegion) %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else (any(unique(cov$BrainRegion) %in% c('CER', 'TCX'))) {
      varOfInterest = c('Diagnosis.Gender', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI',
                        'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                        'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
    }
  }
  contVar = 'Diagnosis.Gender'

>>>>

  # Filter counts and covariates
  cnt = cnt[,cov$SampleID]
  BrainRegion = unique(cov$BrainRegion)
  print(BrainRegion)

@@

  # Perform differential expression between case-control
  if(any(BrainRegion %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                    'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(BrainRegion %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else {
      if (any(BrainRegion %in% c('CER', 'TCX'))) {
        varOfInterest = c('Diagnosis', 'Batch', 'Gender', 'RIN', 'AAD', 'PMI',
                          'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                          'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
      }
    }
  }
  contVar = 'Diagnosis'

@@

  # Perform differential expression between case-control in a gender specific manner
  cov$Diagnosis.Gender = factor(paste(cov$Diagnosis, cov$Gender, sep = '.'))
  if(any(BrainRegion %in% c('DLPFC'))){
    varOfInterest = c('Diagnosis.Gender', 'Batch', 'RIN', 'AAD', 'PMI', 
                      'PCT_CODING_BASES', 'PCT_INTERGENIC_BASES')
  } else {
    if (any(BrainRegion %in% c('FP', 'STG', 'PHG', 'IFG'))){
      varOfInterest = c('Diagnosis.Gender', 'Batch', 'RIN', 'AAD', 'PMI', 
                        'PCT_CODING_BASES', 'PCT_PF_READS_ALIGNED', 'PCT_INTERGENIC_BASES', 
                        'PCT_INTRONIC_BASES', 'RIN2')
    } else {
      if (any(BrainRegion %in% c('CER', 'TCX'))) {
        varOfInterest = c('Diagnosis.Gender', 'Batch', 'RIN', 'AAD', 'PMI',
                          'PCT_INTERGENIC_BASES', 'PCT_INTRONIC_BASES', 
                          'PCT_RIBOSOMAL_BASES', 'PCT_CODING_BASES')
      }
    }
  }
  contVar = 'Diagnosis.Gender'
